---
title: "grillade"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{grillade}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grillade)
```


Create responsive matrix of interactive charts :

```{r}
library(apexcharter)
data(economics, package = "ggplot2")
eco <- tail(economics, 350)

grillade(
  n_col = 2,
  knack(
    cols = 1, cols_sm = "all",
    apex(eco, aes(x = date, y = uempmed), "line")
  ),
  knack(
    cols = 1, cols_sm = "all",
    apex(eco, aes(x = date, y = psavert), "line")
  )
)
```







## Detailed examples

A box to be used in examples:

```{r}
box_example <- function(...) {
  tags$div(
    style = "box-sizing:border-box;border:5px solid #1C6EA4;height:50px;",
    ...
  )
}
```



### Automatic grid

Default is to create as many columns as elements inside `grillade()`

```{r}
grillade(
  box_example("Column 1"),
  box_example("Column 2"),
  box_example("Column 3"),
  box_example("Column 4"),
  box_example("Column 5")
)
```


### Add gutter between columns

Add a space between columns :

```{r}
grillade(
  gutter = TRUE,
  box_example("Column 1"),
  box_example("Column 2"),
  box_example("Column 3"),
  box_example("Column 4"),
  box_example("Column 5")
)
```

Other possible values for `gutter` are `l` or `xl`.


### Fixed number of columns

You specify a number of columns, if the grillade have more elements than that, they will be on the next row :

```{r}
grillade(
  n_col = 3,
  box_example("Column 1"),
  box_example("Column 2"),
  box_example("Column 3"),
  box_example("Column 4"),
  box_example("Column 5")
)
```


### Specific column's width

There's two way to specify custom width for columns, directly in `grillade()`:

```{r}
grillade(
  n_col = 5, 
  cols_width = c(3, 2, NA, 3, "all"),
  box_example("Column 1"),
  box_example("Column 2"),
  box_example("Column 3"),
  box_example("Column 4"),
  box_example("Column 5")
)
```

Note that we defined `5` columns in our grid and first element have width `3`, so it will take 3/5 of the full width.

`NA` correspond to a width of `1`.

Second way to specify widths is using `knack()` to build grid's element:

```{r}
grillade(
  n_col = 5, 
  knack(
    cols = 3,
    box_example("Column 1")
  ),
  knack(
    cols = 2,
    box_example("Column 2")
  ),
  box_example("Column 3"),
  knack(
    cols = 3,
    box_example("Column 4")
  ),
  knack(
    cols = "all",
    box_example("Column 5")
  )
)
```


### Specific row's height

With `knack()` you can also provide row height:


```{r}
grillade(
  n_col = 3,
  knack(
    rows = 2,
    box_example("Column 1", style="height:100px;")
  ),
  box_example("Column 2"),
  box_example("Column 3"),
  knack(
    cols = 2,
    rows = 2,
    box_example("Column 4", style="height:100px;")
  ),
  box_example("Column 5")
)
```


### Responsive

You can specify the number of columns taken for small size screen:

```{r}
grillade(
  n_col = 5, 
  n_col_sm = 2,
  box_example("Column 1"),
  box_example("Column 2"),
  box_example("Column 3"),
  box_example("Column 4"),
  box_example("Column 5")
)
```

Specify each columns width with small media:

```{r}
grillade(
  n_col = 6,
  knack(
    cols = 2, cols_sm = 3,
    box_example("Column 1")
  ),
  knack(
    cols = 2, cols_sm = 3,
    box_example("Column 2")
  ),
  knack(
    cols = 2, cols_sm = 3,
    box_example("Column 3")
  ),
  knack(
    cols = 3, cols_sm = "all",
    box_example("Column 4")
  ),
  knack(
    cols = 3, cols_sm = "all",
    box_example("Column 5")
  )
)
```





