---
title: "rmarkdown usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grillade)
library(apexcharter)
library(ggplot2)
```


## grillade()

You can use `grillade()` in an `rmarkdown::html_document()` to combine multiple {htmlwidgets}, here an example with the [{apexcharter}](https://github.com/dreamRs/apexcharter) package :

```{r}
a1 <- apex(
  data = tail(economics, 350),
  mapping = aes(x = date, y = uempmed),
  type = "line"
)
a2 <- apex(
  data = tail(economics, 350),
  mapping = aes(x = date, y = psavert),
  type = "line"
)

grillade(a1, a2)
```



## With fenced Div

If you want to create columns with content other than something that produce HTML, you can use fence div, but before that you have to load grillade HTML dependencies like that : 

```{r}
# Loading grillade
use_grillade()
```

After that, use `:::: {.autogrid .has-gutter}` to start the grillade (automatic number of columns with a gutter between them) and `::: {}` to delimit columns:

:::: {.autogrid .has-gutter}

::: {}

First plot:

```{r}
ggplot(tail(economics, 350)) +
  geom_line(aes(x = date, y = uempmed))
```

:::

::: {}

Second plot on the left:

```{r}
ggplot(tail(economics, 350)) + 
  geom_line(aes(x = date, y = psavert))
```

:::

::::


Code is :

``````
:::: {.autogrid .has-gutter}

::: {}

First plot:

```r
ggplot(tail(economics, 350)) +
  geom_line(aes(x = date, y = uempmed))
```

:::

::: {}

Second plot on the left:

```r
ggplot(tail(economics, 350)) + 
  geom_line(aes(x = date, y = psavert))
```

:::

::::
``````







